---
title: "exp preference"
author: "Allen Yeh"
output:
  html_document: default
  pdf_document: default
---

```
```

```{r warning=FALSE}
library(tidyverse)
library(gmodels)
library(rstatix)
library(tools)
library(ez)
library(ARTool)
library(emmeans)
```

### Import data

#### Read the csv file and claim the data type
```{r}
run_ids <- c("1", "3", "4", "5", "7", "10", "11", "15", "16", "17", "18", "21", "22", "23", "26", "27", "29", "30")
gesture_level <- c("SHIFT_ABD", "SHIFT_ADD", "SPIN_ABD_HALF", "SPIN_ABD_FULL", "SPIN_ADD_HALF", "SPIN_ADD_FULL", "ROTATE_ABD_HALF", "ROTATE_ABD_FULL", "ROTATE_ADD_HALF", "ROTATE_ADD_FULL", "FLIP_ABD_HALF", "FLIP_ABD_FULL", "FLIP_ADD_HALF", "FLIP_ADD_FULL")
type_level <- c("ease", "comfort", "confidence", "social_acceptance")

data <- read_csv("exp_preference.csv", col_types = cols(
  id = col_integer(),
  gesture = col_factor(levels = gesture_level),
  manipulation = col_factor(levels = c("0", "1", "2", "3")), 
  direction = col_factor(levels = c("0", "1")),
  magnitude = col_factor(levels = c("0", "1", "2")),
  type = col_factor(levels = type_level),
  likert = col_integer()
  )) %>%
    filter(tolower(`id`) %in% run_ids) %>%
  mutate(
    manipulation_code = manipulation %>% recode_factor(
      `3` = "FLIP",  
      `2` = "ROTATE",
      `1` = "SPIN",
      `0` = "SHIFT"
      ),
    direction_code = direction %>% recode_factor(
      `1` = "ADD",
      `0` = "ABD"
      ),
    magnitude_code = magnitude %>% recode_factor(
      `2` = "NONE",
      `1` = "FULL",
      `0` = "HALF"
      ),
)

participants <- read_csv("exp_participants_short_v2.csv", col_types = cols(
  id = col_integer(),
  gender = col_factor(levels = c("Male","Female")), 
  age = col_integer(), 
  phoneExperience = col_factor(levels = c("-3","3-5", "6-10", "10-")),
  screenSize = col_factor(levels = c("-4", "4-5", "5-6", "6-")), 
  dailyUsage = col_factor(levels = c("-1", "1-2", "2-4", "4-8", "8-")), 
  handSize = col_factor(levels = c("5.5-6.5", "6.5-7.5", "7.5-8.5", "8.5-9.5", "9.5-10.5")),
  phoneHeight = col_double(),
  phoneWidth = col_double(),
  phoneThickness = col_double(),
  phoneWeight = col_double()
)) %>%
    filter(tolower(`id`) %in% run_ids) %>% 
  mutate(
    phoneSize_Num = screenSize  %>%  recode(
          "-4" = 1,
          "4-5" = 2,
          "5-6" = 3,
          "6-" = 4
          ),
    handSize_Num = handSize  %>%  recode(
          "5.5-6.5" = 1,
          "6.5-7.5" = 2,
          "7.5-8.5" = 3,
          "8.5-9.5" = 4,
          "9.5-10.5" = 5
          )
      )


res <- cor.test(participants$phoneSize_Num, participants$handSize_Num, 
                    method = "spearman")
res

library("ggpubr")
ggscatter(participants, x = "phoneSize_Num", y = "handSize_Num", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "PhoneSize", ylab = "HandSize")

```

### ease

#### summarize

```{r warning=FALSE}
data_ease <- data %>%
  filter(type == "ease")

boxplot(likert~gesture,data=data_ease, main="Ease",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)

data_ease_summary <-data_ease %>%
  group_by(gesture) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

# line + dot
ease_graph <- ggplot(data_ease_summary) +
  geom_pointrange( aes(x=reorder(gesture, desc(gesture)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

ease_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank()
    )
ggsave("ease_gesture_ci.pdf", width = 7, height = 7)

data_ease_type_summary <-data_ease %>%
  group_by(manipulation) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

# line + dot
ease_type_graph <- ggplot(data_ease_type_summary) +
  geom_pointrange( aes(x=reorder(manipulation, desc(manipulation)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse( lim=c(7,2)) + 
  coord_flip()

ease_type_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank()
    )
ggsave("ease_manipulation_ci.pdf", width = 7, height = 2)

#data_ease_count <- data_ease %>% group_by(manipulation) %>% count(likert)
#write.csv(data_ease_count,"ease_count.csv", row.names = TRUE)
```
#### manipulation x direction

```{r warning=FALSE}
data_md_summary <-data_ease %>%
  group_by(manipulation_code, direction_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_md_summary

data_type_summary <-data_ease %>%
  group_by(manipulation_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_type_summary

total_ease <- full_join(data_ease, participants)

res <- cor.test(total_ease$phoneSize_Num, total_ease$likert, 
                    method = "spearman")
res

res <- cor.test(total_ease$handSize_Num, total_ease$likert, 
                    method = "spearman")
res

res <- cor.test(total_ease$phoneHeight, total_ease$likert, 
                    method = "spearman")
res

res <- cor.test(total_ease$phoneWidth, total_ease$likert, 
                    method = "spearman")
res

res <- cor.test(total_ease$phoneThickness, total_ease$likert, 
                    method = "spearman")
res

res <- cor.test(total_ease$phoneWeight, total_ease$likert, 
                    method = "spearman")
res

library("ggpubr")
ggscatter(total_ease, x = "phoneSize_Num", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "PhoneSize", ylab = "Score")

ggscatter(total_ease, x = "handSize_Num", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "HandSize", ylab = "Score")

ggscatter(total_ease, x = "phoneHeight", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneHeight", ylab = "Score")

ggscatter(total_ease, x = "phoneWidth", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneWidth", ylab = "Score")

ggscatter(total_ease, x = "phoneThickness", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneThickness", ylab = "Score")

ggscatter(total_ease, x = "phoneWeight", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneWeight", ylab = "Score")
```

#### analysis
```{r warning=FALSE}
shapiro.test(data_ease$likert)

m <- art(
  likert ~ manipulation_code*direction_code + (1|id),
  data = data_ease
)

anova(m)

contrast(emmeans(artlm(m,"manipulation_code"), ~ manipulation_code), method="pairwise", adjust="bonferroni")
```
#### manipulation x direction x magnitude
```{r warning=FALSE}
data_anova = data_ease %>%
    filter(manipulation_code != "SHIFT")

data_mag_summary <-data_anova %>%
  group_by(magnitude_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_mag_summary

data_type_summary <-data_anova %>%
  group_by(manipulation_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_type_summary
```

#### analysis
```{r warning=FALSE}
shapiro.test(data_anova$likert)

m <- art(
  likert ~ manipulation_code*direction_code*magnitude_code + (1|id),
  data = data_anova
)

anova(m)

contrast(emmeans(artlm(m,"manipulation_code"), ~ manipulation_code), method="pairwise", adjust="bonferroni")

contrast(emmeans(artlm(m,"magnitude_code"), ~ magnitude_code), method="pairwise", adjust="bonferroni")
```

### comfort
#### summarize

```{r warning=FALSE}
data_comfort <- data %>%
  filter(type == "comfort")

boxplot(likert~gesture,data=data_comfort, main="comfort",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)

data_comfort_summary <-data_comfort %>%
  group_by(gesture) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

# line + dot
comfort_graph <- ggplot(data_comfort_summary) +
  geom_pointrange( aes(x=reorder(gesture, desc(gesture)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

comfort_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank()
    )
ggsave("comfort_gesture_ci.pdf", width = 7, height = 7)

data_comfort_type_summary <-data_comfort %>%
  group_by(manipulation) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

# line + dot
comfort_type_graph <- ggplot(data_comfort_type_summary) +
  geom_pointrange( aes(x=reorder(manipulation, desc(manipulation)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

comfort_type_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank()
    )
ggsave("comfort_manipulation_ci.pdf", width = 7, height = 2)

#data_comfort_count <- data_comfort %>% group_by(manipulation) %>% count(likert)
#write.csv(data_comfort_count,"comfort_count.csv", row.names = TRUE)

```

#### manipulation x direction

```{r warning=FALSE}
data_md_summary <-data_comfort %>%
  group_by(manipulation_code, direction_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_md_summary

data_type_summary <-data_comfort %>%
  group_by(manipulation_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_type_summary

total_comfort <- full_join(data_comfort, participants)

res <- cor.test(total_comfort$phoneSize_Num, total_comfort$likert, 
                    method = "spearman")
res

res <- cor.test(total_comfort$handSize_Num, total_comfort$likert, 
                    method = "spearman")
res

res <- cor.test(total_comfort$phoneHeight, total_comfort$likert, 
                    method = "spearman")
res

res <- cor.test(total_comfort$phoneWidth, total_comfort$likert, 
                    method = "spearman")
res

res <- cor.test(total_comfort$phoneThickness, total_comfort$likert, 
                    method = "spearman")
res

res <- cor.test(total_comfort$phoneWeight, total_comfort$likert, 
                    method = "spearman")
res


library("ggpubr")
ggscatter(total_comfort, x = "phoneSize_Num", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "PhoneSize", ylab = "Score")

ggscatter(total_comfort, x = "handSize_Num", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "HandSize", ylab = "Score")

ggscatter(total_comfort, x = "phoneHeight", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneHeight", ylab = "Score")

ggscatter(total_comfort, x = "phoneWidth", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneWidth", ylab = "Score")

ggscatter(total_comfort, x = "phoneThickness", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneThickness", ylab = "Score")

ggscatter(total_comfort, x = "phoneWeight", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneWeight", ylab = "Score")
```

#### analysis
```{r warning=FALSE}
shapiro.test(data_comfort$likert)

m <- art(
  likert ~ manipulation_code*direction_code + (1|id),
  data = data_comfort
)

anova(m)

contrast(emmeans(artlm(m,"manipulation_code"), ~ manipulation_code), method="pairwise", adjust="bonferroni")
```
#### manipulation x direction x magnitude
```{r warning=FALSE}
data_anova = data_comfort %>%
    filter(manipulation_code != "SHIFT")

data_mag_summary <-data_anova %>%
  group_by(magnitude_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_mag_summary

data_type_summary <-data_anova %>%
  group_by(manipulation_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_type_summary
```

#### analysis
```{r warning=FALSE}
shapiro.test(data_anova$likert)

m <- art(
  likert ~ manipulation_code*direction_code*magnitude_code + (1|id),
  data = data_anova
)

anova(m)

contrast(emmeans(artlm(m,"manipulation_code"), ~ manipulation_code), method="pairwise", adjust="bonferroni")

contrast(emmeans(artlm(m,"magnitude_code"), ~ magnitude_code), method="pairwise", adjust="bonferroni")
```


### confidence
#### summarize

```{r warning=FALSE}
data_confidence <- data %>%
  filter(type == "confidence")

boxplot(likert~gesture,data=data_confidence, main="confidence",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)

data_confidence_summary <-data_confidence %>%
  group_by(gesture) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

# line + dot
confidence_graph <- ggplot(data_confidence_summary) +
  geom_pointrange( aes(x=reorder(gesture, desc(gesture)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#c0392b", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

confidence_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank()
    )
ggsave("confidence_gesture_ci.pdf", width = 7, height = 7)

data_confidence_type_summary <-data_confidence %>%
  group_by(manipulation) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

# line + dot
confidence_type_graph <- ggplot(data_confidence_type_summary) +
  geom_pointrange( aes(x=reorder(manipulation, desc(manipulation)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#c0392b", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

confidence_type_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank()
    )
ggsave("confidence_manipulation_ci.pdf", width = 7, height = 2)

```

#### manipulation x direction

```{r warning=FALSE}
data_md_summary <-data_confidence %>%
  group_by(manipulation_code, direction_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_md_summary

data_type_summary <-data_confidence %>%
  group_by(manipulation_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_type_summary

total_confidence <- full_join(data_confidence, participants)

res <- cor.test(total_confidence$phoneSize_Num, total_confidence$likert, 
                    method = "spearman")
res

res <- cor.test(total_confidence$handSize_Num, total_confidence$likert, 
                    method = "spearman")
res


res <- cor.test(total_confidence$phoneHeight, total_confidence$likert, 
                    method = "spearman")
res

res <- cor.test(total_confidence$phoneWidth, total_confidence$likert, 
                    method = "spearman")
res

res <- cor.test(total_confidence$phoneThickness, total_confidence$likert, 
                    method = "spearman")
res

res <- cor.test(total_confidence$phoneWeight, total_confidence$likert, 
                    method = "spearman")
res


library("ggpubr")
ggscatter(total_confidence, x = "phoneSize_Num", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "PhoneSize", ylab = "Score")

ggscatter(total_confidence, x = "handSize_Num", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "HandSize", ylab = "Score")

ggscatter(total_confidence, x = "phoneHeight", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneHeight", ylab = "Score")

ggscatter(total_confidence, x = "phoneWidth", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneWidth", ylab = "Score")

ggscatter(total_confidence, x = "phoneThickness", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneThickness", ylab = "Score")

ggscatter(total_confidence, x = "phoneWeight", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneWeight", ylab = "Score")

```

#### analysis
```{r warning=FALSE}
shapiro.test(data_confidence$likert)

m <- art(
  likert ~ manipulation_code*direction_code + (1|id),
  data = data_confidence
)

anova(m)

contrast(emmeans(artlm(m,"manipulation_code"), ~ manipulation_code), method="pairwise", adjust="bonferroni")
```
#### manipulation x direction x magnitude
```{r warning=FALSE}
data_anova = data_confidence %>%
    filter(manipulation_code != "SHIFT")

data_mag_summary <-data_anova %>%
  group_by(magnitude_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_mag_summary

data_type_summary <-data_anova %>%
  group_by(manipulation_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_type_summary
```

#### analysis
```{r warning=FALSE}
shapiro.test(data_anova$likert)

m <- art(
  likert ~ manipulation_code*direction_code*magnitude_code + (1|id),
  data = data_anova
)

anova(m)

contrast(emmeans(artlm(m,"manipulation_code"), ~ manipulation_code), method="pairwise", adjust="bonferroni")

contrast(emmeans(artlm(m,"magnitude_code"), ~ magnitude_code), method="pairwise", adjust="bonferroni")
```


### social acceptance
#### summarize

```{r warning=FALSE}
data_social <- data %>%
  filter(type == "social_acceptance")

boxplot(likert~gesture,data=data_social, main="social_acceptance",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)

data_social_summary <-data_social %>%
  group_by(gesture) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

# line + dot
social_graph <- ggplot(data_social_summary) +
  geom_pointrange( aes(x=reorder(gesture, desc(gesture)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#5d6d7e", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

social_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank()
    )
ggsave("social_acceptance_gesture_ci.pdf", width = 7, height = 7)

data_social_type_summary <-data_social %>%
  group_by(manipulation) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

# line + dot
social_type_graph <- ggplot(data_social_type_summary) +
  geom_pointrange( aes(x=reorder(manipulation, desc(manipulation)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#5d6d7e", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

social_type_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank()
    )
ggsave("social_acceptance_manipulation_ci.pdf", width = 7, height = 2)
```

#### manipulation x direction

```{r warning=FALSE}
data_md_summary <-data_social %>%
  group_by(manipulation_code, direction_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_md_summary

data_type_summary <-data_social %>%
  group_by(manipulation_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_type_summary

total_social <- full_join(data_social, participants)

res <- cor.test(total_social$phoneSize_Num, total_social$likert, 
                    method = "spearman")
res

res <- cor.test(total_social$handSize_Num, total_social$likert, 
                    method = "spearman")
res


res <- cor.test(total_social$phoneHeight, total_social$likert, 
                    method = "spearman")
res

res <- cor.test(total_social$phoneWidth, total_social$likert, 
                    method = "spearman")
res

res <- cor.test(total_social$phoneThickness, total_social$likert, 
                    method = "spearman")
res

res <- cor.test(total_social$phoneWeight, total_social$likert, 
                    method = "spearman")
res



library("ggpubr")
ggscatter(total_social, x = "phoneSize_Num", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "PhoneSize", ylab = "Score")

ggscatter(total_social, x = "handSize_Num", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "HandSize", ylab = "Score")

ggscatter(total_social, x = "phoneHeight", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneHeight", ylab = "Score")

ggscatter(total_social, x = "phoneWidth", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneWidth", ylab = "Score")

ggscatter(total_social, x = "phoneThickness", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneThickness", ylab = "Score")

ggscatter(total_social, x = "phoneWeight", y = "likert", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "phoneWeight", ylab = "Score")
```

#### analysis
```{r warning=FALSE}
shapiro.test(data_social$likert)

m <- art(
  likert ~ manipulation_code*direction_code + (1|id),
  data = data_social
)

anova(m)

contrast(emmeans(artlm(m,"manipulation_code"), ~ manipulation_code), method="pairwise", adjust="bonferroni")
```
#### manipulation x direction x magnitude
```{r warning=FALSE}
data_anova = data_social %>%
    filter(manipulation_code != "SHIFT")

data_mag_summary <-data_anova %>%
  group_by(magnitude_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_mag_summary

data_type_summary <-data_anova %>%
  group_by(manipulation_code) %>%
  summarize(
    meanScore = likert %>% mean(na.rm=TRUE),
    lowCI = ci(likert)[2]%>% pmax(0),
    highCI = ci(likert)[3],
    sd = ci(likert)[4],
    std = likert %>% sd())

data_type_summary
```

#### analysis
```{r warning=FALSE}
shapiro.test(data_anova$likert)

m <- art(
  likert ~ manipulation_code*direction_code*magnitude_code + (1|id),
  data = data_anova
)

anova(m)

contrast(emmeans(artlm(m,"manipulation_code"), ~ manipulation_code), method="pairwise", adjust="bonferroni")

contrast(emmeans(artlm(m,"magnitude_code"), ~ magnitude_code), method="pairwise", adjust="bonferroni")
```

